---
title: "Instacart_EDA"
author: "Tianyi Fang"
date: "January 24, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
On its website Instacart has a recommendation feature, suggesting the users some items that he/she may buy again. Our task is to predict which items will be reordered on the next order.
The dataset consists of information about 3.4 million grocery orders, distributed across 6 csv files.
****SQL*******
SQL is to store and manage large database.DML:data manipulation language:select/update/insert/delete(during using table); DDL:data definition language: create/drop/alter>>to define or change the structure/data type/relationship/constrains of tables(during creating table)
So use SQL to separate related informations into different tables(order_details; user_details, product_details...). All of these tables are related by primary/foriegn keys. Using SQL quickly get an idea of the entire dataset(top products among young customer/best sell region/period), 
****Tableau*****
In order to better present to other teams/managers, we'd like to visualize what we found. Using Tableau. 
everyday selling:using scattering plot along month(add monthly avg+total avg)>> see the trend(
???result???peak during mid year(some festivals), end year(big sales), increase from last year). 
Difference between different customer segments:
based on gender, age, region to see how different are their shopping habbits(time, popular product, frequency)
???result???:1.female obviously higher than male, especially in daily products(food, health beauty, household), but among some categories(electronic, auto, equipment, sports) male is higher. The total/ avg/ frequency differ from regions among gender and ages.
2. Young buyer almost buy everything(including fresh fruit, meat, seafood, cooked food, beauty, makeup, tissue paper...) elder buyers prefer non-food, very low in fresh food/meat department.>>Reason>>customer survey>>how to promote?(information, free trial/delivery)
Difference between different products:
Based on aisles, department, region>>find the popular one/reorder products
purchase propotion/reorder rate/quantity/trend>>deal with supplier/ better sales preiod selling prediction, )
*****Exploratory Data Aanalysis******

```{r}
library(data.table)
library(dplyr)
library(ggplot2)
library(knitr)
library(stringr)
library(DT)
```
1.1 read in data
```{r}
#
orders <- read.csv("orders.csv", header = T, stringsAsFactors = FALSE)

order_product <- read.csv("order_products__train.csv", header = T, stringsAsFactors = FALSE)

products <- read.csv("products.csv", header = T, stringsAsFactors = FALSE)
departments <- read.csv("departments.csv", header = T, stringsAsFactors = TRUE)
aisles <- read.csv("aisles.csv", header = T, stringsAsFactors = TRUE)
order_product_prior <- read.csv("order_products__prior.csv", header = T, stringsAsFactors = FALSE)
#take a look
head(orders, 12)
str(orders)
summary(orders)
head(products, 12)
head(order_product, 12)
```
1.2 convert data type
```{r}
orders <- orders %>% mutate(order_hour_of_day = as.numeric(order_hour_of_day), eval_set = as.factor(eval_set))
products <- products %>% mutate(product_name = as.factor(product_name))
aisles <- aisles%>%mutate(aisle = as.factor(aisle))
departments <- departments %>% mutate(department = as.factor(department))
```
2. Analysis
2.1 Shopping Time of a day
```{r}
orders %>% ggplot(aes(x = order_hour_of_day)) + geom_histogram(stat = "count")
#find during the daytime, from 9 to 17 is the shopping peak.()
orders %>% ggplot(aes(x = order_dow)) + geom_histogram(stat = "count")
#Weekends are shopping peak.
#using Tableau, know which period of a week is high time
```
When do they order again?
```{r}
orders %>% ggplot(aes(x = days_since_prior_order)) + geom_histogram(stat = "count", fill = "dark blue") + geom_vline(xintercept = quantile(orders$days_since_prior_order, 0.8, na.rm = TRUE) , linetype = "dotted", color = "red", size = 1.5)
#most customers do reorder within one week

```
What's the avg order times per customer?
```{r}
length(unique(orders$order_id))
orders %>% group_by(order_id) %>% 
  summarize(avg_order = mean(last(order_number))/length(unique(order_id)))%>%
  ggplot(aes(x = avg_order)) + 
  geom_histogram(stat = "count", fill = "dark blue")+ geom_vline(xintercept = quantile(avg_order, 0.8, na.rm = TRUE), linetype = "dotted", color = "red", size = 1.5) labs(title = "What's the average order times per customer?")
#most customers do 
```
How many items do people buy?
```{r}
item <- order_product %>%
  group_by(order_id) %>%
  summarize(n_items = last(add_to_cart_order))
item %>%
  ggplot(aes(x = n_items)) + 
  geom_histogram(stat="count", fill = "dark blue") + geom_vline(xintercept = quantile(item$n_items, 0.8, na.rm = TRUE), linetype = "dotted", color = "red", size = 1.5)+ coord_cartesian(xlim = c(0,60))+ labs(title = "How many items per order?")
#the avg items per order are around 1~10
```
what is the bestseller?
10 Most popular products
```{r}
#combine tables
tmp <- order_product%>%
  group_by(product_id)%>%
  summarize(count = n()) %>%
  top_n(20, wt = count) %>%
  left_join(select(products, product_id, product_name), by = "product_id") %>%
  arrange(desc(count))
tmp
#banana is the most popular products, and all of the top ten are fresh fruit, more than half of them are organic products. Seems really healthy>>might insight about the customer portfolio: prefer healthy, organic food, wealthy and busy. In top 200, 14 are organic. 
#why banana? Healthy, cheapest, no risk of bad quality;>>do customer survey
tmp%>% ggplot(aes(x = reorder(product_name, -count), y = count))+ 
  geom_bar(stat = "identity", fill = "dark blue")+ theme(axis.text.x = element_text(angle = 50, hjust = 1), axis.title.x = element_blank())+ labs(title = "Top 20 products")
```

How often do people order the same items again?
```{r}
tmp <- order_product %>%
  group_by(reordered) %>%
  summarize(count = n()) %>%
  mutate(reordered = as.factor(reordered))%>%
  mutate(proportion = count/sum(count))
tmp %>% ggplot(aes(x = reordered, y = count, fill = reordered)) + geom_bar(stat ="identity")
```
Most often reordered items
```{r}
tmp <- order_product %>%
  group_by(product_id) %>%
  summarize(proportion_reordered = mean(reordered), n = n()) %>%
  filter(n > 40) %>%
  top_n(10, wt = proportion_reordered) %>%
  arrange(desc(proportion_reordered))%>%
  left_join(products, by = "product_id")
tmp
tmp %>%
  ggplot(aes(x = reorder(product_name, -proportion_reordered), y = proportion_reordered)) + geom_bar(stat = "identity", fill = "dark blue") + theme(axis.text.x=element_text(angle=50, hjust=1), axis.title.x = element_blank()) + coord_cartesian(ylim = c(0.85,0.95)) + labs(title = "Top 10 reordered items")
```
Which item do people put into cart first?
```{r}
tmp <- order_product %>%
  group_by(product_id, add_to_cart_order) %>%
  summarize(count = n())%>%
  mutate(precent = count/sum(count)) %>%
  filter(add_to_cart_order ==1,  count >10) %>%
  arrange(desc(precent)) %>%
  left_join(products, by = "product_id") %>%
  select(product_name, precent, count) %>%
  ungroup()%>%
  top_n(10, wt = precent)
tmp %>%
  ggplot(aes(x = reorder(product_name, -precent), y = precent)) +
  geom_bar(stat = "identity", fill = "dark blue") + theme(axis.text.x=element_text(angle=50, hjust=1), axis.title.x = element_blank()) + coord_cartesian(ylim = c(0.4,0.7)) + labs(title = "Items added to cart first")
#2%Lactose Free Milk is the most popular reorder product and 5th to be added to cart.
```

Association between time of last order and probability of reorder
```{r}
order_product %>%
  left_join(orders, by = "order_id") %>%
  group_by(days_since_prior_order) %>%
  summarize(mean_reorder = mean(reordered)) %>%
  ggplot(aes(x = days_since_prior_order, y = mean_reorder)) + geom_bar(stat = "identity", fill = "dark blue")
#Not so muc pattern of it. as days go by, people tend to buy new items instead of reordered.
```
Association between # of orders and Prob. of reordering
```{r}
order_product %>%
  group_by(product_id) %>%
  summarize(proportion_reordered = mean(reordered), n = n()) %>%
  ggplot(aes(x = n, y = proportion_reordered)) + geom_point() + geom_smooth(color = "red") +coord_cartesian(xlim = c(0,2000))
#less items per order, more to be reordered. Probably if buy too many things at one time, then many items are not satisfied, so will not be reordered again.
```
Organic/Non-Organic
```{r}
product <- products %>%
  mutate(organic = ifelse(str_detect(str_to_lower(products$product_name), 'organic'),'organic', 'non-organic'), organic = as.factor(organic))
tmp <- order_product %>%
  left_join(product, by = "product_id") %>%
  group_by(organic) %>%
  summarize(count = n()) %>%
  mutate(proportion = count/sum(count))
tmp
tmp %>%
  ggplot(aes(x = organic, y =count, fill = organic)) +geom_bar(stat = "identity") +labs(title = "Ordered Products of Organic/Non-Organic")
```
Reordered products Organic/Non Organic
```{r}
tmp <- order_product %>% left_join(product, by = "product_id") %>% group_by(organic) %>% summarize(mean_reordered = mean(reordered))
tmp %>% ggplot(aes(x = organic, fill = organic, y = mean_reordered)) +geom_bar(stat = "identity")+labs(title = "Rerdered Products of Organic/Non-Organic")


```

Exploring customer habits
Focus on reorders
```{r}
#eliminate the first order
tmp <- order_product_prior%>%
  group_by(order_id) %>%
  summarize(mean = mean(reordered), n = n()) %>%
  right_join(filter(orders, order_number >2), by = "order_id")
tmp
tmp2 <- tmp %>%
  filter(eval_set == "prior") %>%
  group_by(user_id) %>%
  summarize(n_equal = sum(mean ==1, na.rm = T), percent_equal = n_equal/n()) %>%
  filter(percent_equal == 1) %>%
  arrange(desc(n_equal))
tmp2
head(tmp2)
#these customers are who only buy 1 item per order, check what they bought
```


```{r}
uo <- filter(tmp, user_id == 99753)$order_id
tmp3 <- order_product_prior %>%
  filter(order_id %in% uo) %>%
  left_join(product, by = "product_id")

result <- select(tmp3, -aisle_id, -department_id, -organic)
result 

```

take a look at what he bought in the train set
```{r}
tmp4 <- orders %>% filter(user_id == 99753, eval_set == "train")
tmp5 <- order_product %>%
  filter(order_id == tmp4$order_id)%>%
  left_join(product, by = "product_id")
result2 <- select(tmp5, -aisle_id, -department_id, -organic)
result2 
#he is a big fan of organic milk!!!
```
