---
title: "Zillow_model_try"
author: "Tianyi Fang"
date: "October 13, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Linear Regression

```{r}
lm.dataset <- read.csv("train_property.csv", header=TRUE, stringsAsFactors = FALSE)
mod1 <- lm(logerror~
            tax_property+ sqrt_lot+ sqrt_cal_area+ id_census.block+
             year_built+ cnt_bathr+cnt_bedr+fips, data=lm.dataset)
summary(mod1)
train.sub <- lm.dataset[, c("logerror","cnt_bathr", "cnt_bedr","fips", "type_landuse",
                            "id_rawcensus_block", "region_county", "cnt_room","tax_total", "tax_land","tax_property",
                            "tax_building","sqrt_cal_area","year_built", "region_city", "sqrt_finished_liv", "sqrt_lot")]
mod.t <- lm(logerror~., data=train.sub)
#tax_property, sqrt_cal_area, region_zip
alias(mod1)
summary(mod.t)
#remove all NA
train.sub <-train.sub[which(apply(train.sub,1,function(x) length(which(is.na(x)))==0)), ]
#type_landuse, tax_total, tax_property, region_zip, sqrt_cal_area

mod.lm.b <- lm(logerror~
            tax_property+ sqrt_cal_area+ region_zip, data=lm.dataset)
summary(mod.lm.b)
```
The simple linear regression model will contains tax_property, sqrt_cal_area, region_zip and code_landuse, but their coefficient are quite small, and also several levels of code_landuse are shown as features. Next we may try ridge/lasso regression for better model generation.
####standardize
```{r}
train.sub[,-1] <-scale(train.sub[,-1])
mod2 <- lm(logerror~., data=train.sub)
summary(mod2)
names(mod2)
plot(mod2$fitted.values, mod2$residuals, xlab="Fitted",ylab="residual")
```


####use glmnet
```{r}
library(glmnet)
#train.sub$region_zip <- as.character(train.sub$region_zip)
ind <- model.matrix(~., train.sub[,-1])
dep <- train.sub$logerror
fit <- glmnet(x=ind, y=dep)
plot(fit)
#top row indicates the number of nonezero coefficients at the current lamda, which is the effective df for lasso. y is the value of coefficients
plot(fit, xvar="lambda", lab=T)
names(fit)
#get the coefficients of each parameters
coef(fit)[,10]
#from the plot we can try lambda = 4, lambda =8, to see which lambda is better
coef(fit, s=1/exp(4))
#nothing show for lambda=4
coef(fit, s=1/exp(8))
```
we can see the  cnt_bedr, type_landuse, region_county, tax_total, tax_building, tax_property, sqrt_cal_area, sqrt_finished_liv, sqrt_lot have large lambda, which may be penalted.
```{r}

#cross validation toselect lambda
cv.fit <- cv.glmnet(x=ind, y=dep)
plot(cv.fit)
```
The recomment lambda is 14
```{r}
best.lambda <- cv.fit$lambda.min
se.lambda <- cv.fit$lambda.1se
coef(cv.fit, s= best.lambda)
#select the best lambda to get the coefficients 
coef(cv.fit, s = se.lambda)
```
Due to limited time, the feature engineering and model selection are not well done. Still got questions to be figured out.
